beautier: BEAUti for R

### 2017-12-22 article.tex
Before sending out

\title{beautier: BEAUti for R}
\author{Rich\`el J.C. Bilderbeek}

@@

BEAUti does not allow yet that an inferred phylogeny's crown age is fixed.
In an emperical context, a phylogeny's crown age is one of the estimated
parameters. For theoretical work, a fixed and known crown age can result
in a cleaner analysis. \verb;beautier; allows to specify a fixed crown age.

@@

\verb;beautier; creates site models, clock models and tree priors with the same default distrbutions as BEAUti.
For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity
to infinity. This assumption entails that negative and positive birth rates are just as likely, where a negative birth rate is biologically impossible. 
One may prefer to have an exponential distribution instead, as this would state that birth rates are always positive, and
higher values are less likely than lower values. To do so \verb;beautier; is shown by listing \ref{lis:diff_distr}:

@@

\verb;beautier;'s development takes place on GitHub \cite{github}. 
GitHub is a website that hosts (among others) software and facilites its development.
Using GitHub is a good practice for computational scientists \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.

\verb;beautier;'s quality is assured by Travis CI \cite{travis}. Travis CI is
a continuous integration service, that runs a script upon a (suggested)
change in \verb;beautier;'s code. The \verb;beautier; script checks if the
package can be build, runs all unit and intergration tests, 
measures code coverage, coding style and good practices.

Unit and integration tests check the intergrity of \verb;beatier;. All functions
are tested for producing the correct output and desired error handling. 
Travis CI uses the testing facilities of the \verb;testthat; \cite{testthat} package.

@@

Coding style is the way statements are laid out, for example the placement of 
curly brackets. \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}. 
Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style
is used.

>>>>

\title{beautier: BEAUti for R}
\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}

@@

BEAUti does not allow yet that an inferred phylogeny's crown age is fixed.
In an empirical context, a phylogeny's crown age is one of the estimated
parameters. For theoretical work, a fixed and known crown age can result
in a cleaner analysis. \verb;beautier; allows to specify a fixed crown age.

@@

\verb;beautier; creates site models, clock models and tree priors with the same default distributions as BEAUti.
For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity
to infinity. This assumption entails that negative and positive birth rates are just as likely, where a negative birth rate is biologically impossible. 
One may prefer to have an exponential distribution instead, as this would state that birth rates are always positive, and
higher values are less likely than lower values. To do so \verb;beautier; is shown by listing \ref{lis:diff_distr}:

@@

\verb;beautier;'s development takes place on GitHub \cite{github}. 
GitHub is a website that hosts (among others) software and facilitates its development.
Using GitHub is a good practice for computational scientists \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.

\verb;beautier;'s quality is assured by Travis CI \cite{travis}. Travis CI is
a continuous integration service, that runs a script upon a (suggested)
change in \verb;beautier;'s code. The \verb;beautier; script checks if the
package can be build, runs all unit and integration tests, 
measures code coverage, coding style and good practices.

Unit and integration tests check the integrity of \verb;beatier;. All functions
are tested for producing the correct output and desired error handling. 
Travis CI uses the testing facilities of the \verb;testthat; \cite{testthat} package.

@@

Coding style is the way statements are laid out, for example the placement of 
curly brackets. \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}. 
Travis CI uses the \verb;lintr; \cite{lintr} package to confirm this coding style
is used.
